MSB104_assignment1

### 2023-10-12 MSB104_assignment1.qmd
Update 12.10.23

```{r}
#| label: setup
#| output: false
#| message: false
#| echo: false
library(eurostat)
library(dineq)
library(tidyverse)
library(gridExtra)
library(modelr)
library(grid)
library(ggplotify)
library(vtable)
library(dplyr)
library(dineq)
```

>>>>

```{r}
#| label: setup
#| output: false
#| message: false
#| echo: false
library(eurostat)
library(dineq)
library(tidyverse)
library(gridExtra)
library(modelr)
library(grid)
library(ggplotify)
library(vtable)
library(dplyr)
library(dineq)
library(quarto)
```
